%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
    \cventry
    {People \& Culture Coordinator} % Position
    {Qisetna} % Title
    {London, United Kingdom} % Location
    {March 2025 - Present} % Date
    { % Description
        Qisetna is a cultural initiative dedicated to preserving the oral and cultural heritage of displaced and migrant communities, particularly Syrians, through storytelling and the arts. 
        \vspace{5mm}
        \begin{cvitems}
           \item blah
        \end{cvitems}
    }

    \cventry
    {People \& Culture Coordinator} % Position
    {Bounce - Middle East} % Title
    {Doha, Qatar} % Location
    {September 2021 - June 2023} % Date
    { % Description
        Bounce is a trampoline park and entertainment company head quartered in Dubai with locations across the Middle East. Reporting to the Head of People \& Culture based in Dubai, I was responsible for managing HR operations for 60 employees in Qatar.
        \vspace{5mm}
        \begin{cvitems}
            \item \textbf{Maintained 100\% compliance with Qatar's regulatory standards} by meticulously managing contracts, permits, and documentation, significantly reducing audit risks and ensuring operational continuity.
            \item \textbf{Recruited and onboarded 15 key employees post-COVID}, driving a marked increase in operational efficiency and team performance.
            \item \textbf{Processed monthly payroll for full-time and part-time staff} with precision, consistently delivering accurate compensation and timely bonuses, minimizing discrepancies.
            \item \textbf{Streamlined the onboarding experience} by developing comprehensive orientation programs and training, ensuring smooth transitions for new hires and boosting early-stage engagement.
            \item \textbf{Handled visa applications, travel arrangements, and residence permits} for international hires, ensuring full compliance with local immigration laws and a seamless relocation process.
            \item \textbf{Achieved a 66\% reduction in work permit issuance time} by ensuring complete and accurate documentation, significantly enhancing the efficiency of the hiring process and compliance management.
            \item \textbf{Developed and distributed a handbook of company policies}, empowering employees to effectively resolve workplace conflicts and fostering a positive work environment.
        \end{cvitems}
    }

    \cventry
    {Human Resources Intern}
    {Morison Menon Chartered Accountants \& Partners LLC}
    {Doha, Qatar}
    {March 2021 - May 2021}
    {
        \begin{cvitems}
            \item \textbf{Collaborated with the HR manager} to \textbf{shortlist, interview, and recruit staff} for the accountancy department, contributing to a streamlined hiring process.
            \item \textbf{Maintained and updated employee databases}, ensuring accurate and up-to-date records of passport copies, national IDs, and
            educational documents.
            \item \textbf{Renewed employee contracts}, incorporating new clauses in alignment with QFC and Qatar labor laws, ensuring full legal compliance.
            \item \textbf{Managed the company's LinkedIn and Indeed accounts}, drafting clear and detailed job descriptions for various positions enhancing employer branding and driving increased candidate engagement.
            \item \textbf{Prepared and standardised official HR forms and developed an onboarding checklist} to streamline HR processes and support new hires.
            \item \textbf{Processed payroll for interns}, ensuring timely and accurate compensation while gaining hands-on experience in payroll management.        
        \end{cvitems}
    }


    % \cventry
    % {Business Consultancy Intern} % Position
    % {Morison Menon Chartered Accountants \& Partners LLC} % Company
    % {Doha, Qatar} % Location
    % {February 2021 - March 2021} % Date(s)
    % {
    %     \begin{cvitems} % Description(s) bullet points
    %         \item Collaborated on high-profile client projects, including Al Majlis Sealine Beach Resort, ITAG Qatar, Salam Petroleum, and Goodwin
    %         Qatar, driving strategic initiatives that led to measurable improvements in operational efficiency and profitability.
    %         % \item Led the planning and execution of business consultancy projects, conducting in-depth market research and comprehensive client
    %         % assessments, which directly informed and optimized project strategies.
    %         % \item Performed rigorous feasibility studies, efficiency assessments, and financial projections, providing clients with actionable insights that resulted in data-driven decision-making and enhanced financial performance.
    %         \item Executed detailed SWOT analyses and Porter's Five Forces models, and designed executive-level PowerPoint presentations that shaped strategic business plans and supported high-stakes decision-making. 
    %     \end{cvitems}
    % }
    
%---------------------------------------------------------
\end{cventries}
